BetweenExpDifferences

### 2016-01-26 analysis/BetweenExpDifferences.Rmd
starting pragmatic listener data gathering

## Get all L0 listener data
```{r}

# readLiteralListenerData()
# filesPath :: path to directory with .json files ("../production-results/e8/")
readLiteralListenerData <- function(filesPath) {
  files <- dir(filesPath, pattern = "*.json")
  dRaw <- data.frame()

@@

>>>>

## Get all L0 listener data
```{r}
# readLiteralListenerData()
# -------------------------
# filesPath :: path to directory with .json files ("../production-results/e8/")
readLiteralListenerData <- function(filesPath) {
  files <- dir(filesPath, pattern = "*.json")
  dRaw <- data.frame()

@@

# Pragmatic listener data
```{r}
# readPragmaticListenerData()
# -------------------------
# filesPath :: path to directory with .json files ("../production-results/e8/")
readPragmaticListenerData <- function(filesPath) {
  files <- dir(filesPath, pattern = "*.json")
  dRaw <- data.frame()

  if (grepl("e6", filesPath)) {
    for (f in files) {
      jf <- paste(filesPath, f, sep="")
      jd <- fromJSON(paste(readLines(jf), collapse=""))
      id <- data.frame(workerid = jd$WorkerId, 
                       scale = jd$answer$scale,
                       degree = jd$answer$degree,
                       stars = as.numeric(jd$answer$judgment),
                       language = jd$answer$language)
      dRaw <- bind_rows(dRaw, id)
    }
  } else if (grepl("e11", filesPath)) {
    for (f in files) {
    jf <- paste(filesPath, f, sep="")
    jd <- fromJSON(paste(readLines(jf), collapse=""))
    id <- data.frame(workerid = jd$WorkerId, 
                     scale = jd$answer$data$scale,
                     degree = jd$answer$data$degree,
                     stars = as.numeric(jd$answer$data$judgment),
                     language = jd$answer$data$language)
    dRaw <- bind_rows(dRaw, id)
    }
  } else stop("Must enter 'e6' or 'e11' for exp")

  dRaw
}
e6 <- readPragmaticListenerData("../production-results/e6/")
e11 <- readPragmaticListenerData("../production-results/e11/")
```
